---
title: "Project component 1: Research question proposal"
author: "Aidan Combs"
editor: visual
---

# Project proposal {#proposal}

Please [see this page for instructions](https://soc333-sum23.github.io/project-proposal.html) on how to write your project proposal. Put your work in this document. Render the document and commit your changes regularly ([see instructions here](https://soc333-sum23.github.io/computing-clonerepo.html#how-to-commit-and-push-changes)). When you are done, push your changes to GitHub.

Please write both research questions and their accompanying supporting information and push your work to GitHub before class on Thursday, May 25.

Then, by Tuesday, May 30th, incorporate your peers' feedback into your initial work and add your thoughts on which question you will move forward with (details on the version to submit for grading [can be found here](https://soc333-sum23.github.io/project-proposal.html#version-to-submit-for-grading-tuesday-may-30-1159pm)).

## Setup

In the YAML at the top of the page, replace my name under `author` with yours.

Install the `tidyverse` and `openintro` packages by running the code chunk below (click the green play button). This only needs to be done once.

```{r, eval = FALSE}
install.packages("tidyverse")
install.packages("openintro")
```

Then load them with the `library` function by running the code chunk below. This needs to be done once per session (ie, once each time you open this document).

```{r}
library(tidyverse)
library(openintro)
```

## Research question 1

Write your first research question and provide the requested supporting information here (delete this line).

Use the code block below to generate a `glimpse` of the data you would use to answer this research question (replace `lizard_run` with the name of your dataset, then run the chunk).

```{r}
glimpse(lizard_run)
```

## Research question 2

Write your second research question and provide the requested supporting information here (delete this line).

Use the code block below to generate a `glimpse` of the data you would use to answer this research question (replace `lizard_run` with the name of your dataset).

```{r}
glimpse(lizard_run)
```

## Post-peer review reflections

After class on 5-30, add [your concluding thoughts](https://soc333-sum23.github.io/project-proposal.html#version-to-submit-for-grading-tuesday-may-30-1159pm) about your research questions here (delete this line).
